Technical Report

### 2018-06-13 fully-abstract-comp/technical-report.tex
Updated semantics of scall, so it matches what the implementation does when one of the registers is the temp register.
typo
Refactored one case of the value relation slightly.
Tentative reformulation of reasonability requirements...

>>>>

\subsection{Alternative formulation of reasonability?}
\label{sec:reasonability}

\dominique{The below is an experimental reformulation of the reasonability requirement for the FTLR and full abstraction formulation.  All remarks welcome..
  The main change is that it now says that after a call, the post-return code is also expected to behave reasonably under reasonable assumptions. 
}
\dominique{TODO: better name than ``reasonable'' for all of this.}
Take a block of code memory $\mscode$, a set of trusted addresses $\ta$ and sets of return pointer and closure seals $\sigrets$ and $\sigcloss$.
We define that a word $w$ is reasonable if the following implications hold.
\begin{itemize}
\item If $w = \seal{\sigma_\baddr,\sigma_\eaddr,\_}$, then $[\sigma_\baddr,\sigma_\eaddr] \mathrel{\#} (\sigrets \cup \sigcloss)$
\item If $w = ((\perm,\_),\baddr,\eaddr,\_)$ then $[\baddr,\eaddr] \# \ta$
\item If $w = \sealed{\sigma,\vsc}$ and $\sigma \not\in (\sigrets\cup \sigcloss)$ then $\vsc$ is reasonable.
\end{itemize}

We say that an executable capability $c = ((\perm,\normal),\baddr,\eaddr,\aaddr)$ and data capability $c_{\mathrm{data}}$ behaves reasonably with stack assumption $\ms_\stk'$ up to $n$ steps if the following implication holds:

For any $\Phi$ such that
  \begin{itemize}
  \item $\Phi.\reg(\pcreg) = c$
  \item $\Phi.\reg(\rdata) = c_{\mathrm{data}}$
  \item $\Phi.\reg(r)$ is reasonable for all $r \not\in \{\pcreg,\rdata\}$
  \item $\Phi.\mem(a)$ is reasonable for all $a$
  \item $\Phi.\ms_\stk$ is reasonable for all $a$
  \item $\Phi.\ms_\stk|_{\dom(\ms_\stk')} = \ms_\stk'$
  \item $\Phi.\mem$, $\Phi.\ms_\stk$ and $\Phi.\stk$ are all disjoint
  \end{itemize}
  We have the following implications:
  \begin{itemize}
  \item[Guarantee stack base address before call] If
    \begin{itemize}
    \item $\Phi \nstep[i]{\ta,\stkb} \Phi'$
    \item $\Phi'$ points to $\src{\scall{\offpc,\offsigma}{r_1}{r_2}}$ in $\ta$ for some $\src{r_1}$ and $\src{r_2}$
    \end{itemize}
    Then all of the following hold:
    \begin{itemize}
    \item $\src{\Phi'}(\src{r_\stk}) = \src{\stkptr{\_,\stkb,\eaddr_\stk,\aaddr_\stk}}$
    \item $r_1' \neq \rtmp{1}$
    \item $\Phi'(\pcreg) + \calllen$ and $\Phi'(\rstk)$ behave reasonably with stack assumption $\Phi.\ms_\stk|_{[\eaddr_\stk,\aaddr_\stk]}$ up to $n-i$ steps
    \end{itemize}
  \item[Use return seals only for calls] If
    \begin{itemize}
    \item $\Phi \nstep[i]{\ta,\stkb} \Phi'$
    \item $\src{\Phi'}$ points to $\src{\tcseal{r_1}{r_2}}$ in $\ta$ and $\Phi'(r_1) = \seal{\sigma_\baddr,\sigma_\eaddr,\sigma}$
    \end{itemize}
    Then one of the following holds:
    \begin{itemize}
    \item $\src{\Phi'}$ is inside $\src{\scall{\offpc,\offsigma}{r_1'}{r_2'}}$ and $\sigma \in \sigrets$ 
    \item $\sigma \in \sigcloss$.
    \end{itemize}
  \item[Don't store private stuff...] If
    \begin{itemize}
    \item $\Phi \nstep[i]{\ta,\stkb} \Phi'$
    \item $\src{\Phi'}$ points to $\src{\tstore{r_1}{r_2}}$ in $\ta$, then 
    \end{itemize}
    Then $\Phi.\reg(r_2)$ is reasonable
  \item[Don't leak private stuff...] If
    \begin{itemize}
    \item $\Phi \nstep[i]{\ta,\stkb} \Phi' \step \Phi''$
    \item $\src{\Phi'}$ is in $\ta$
    \item $\src{\Phi''}$ is not in $\ta$
    \end{itemize}
    Then $\Phi.\reg(r)$ is reasonable for all $r$ (including $\pcreg$)
  \end{itemize}

We say that a component $(\mscode,\msdata,\overline{c_{\mathrm{import}}},\overline{c_{\mathrm{export}}},\sigrets,\sigcloss,A_\linear)$ is reasonable if the following hold:
For all $\sealed{\sigma,\vsc},\sealed{\sigma,\vsc'} \in \overline{c_{\mathrm{export}}}$, with $\exec{\vsc}$ and $\nonExec{\vsc'}$, we have that $\vsc$ and $\vsc'$ behave reasonably with stack assumption $\emptyset$ up to any number of steps $n$.
